Improving phase-matching of FWM with temperature

### 2015-09-17 latex/article.tex
formulae again

\subsubsection*{Solution in linear dielectric medium}
A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field:
\begin{equation}
\textbf{P} = \varepsilon_0 \chi \textbf{E}
\end{equation}
where $\chi$ is the susceptibility of the medium and $\varepsilon_r \equiv 1+\chi$ is the relative dielectric constant.

@@

Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P})
\begin{equation}
	\nabla^2 \textbf{E} - \frac{n^2}{c^2}\frac{\partial^2 \textbf{E}}{\partial t^2} = 0
	\label{eq_helm_lin}
\end{equation}
Moreover, $n$ represent the ratio between the speed of light in vacuum and in the material $n = c/v$ and it depends on the frequency of the EM wave.

@@

\vspace{18pt}
**** ripresa delle eq di maxwell?

**** soluzione generale: onde TE, TM
\vspace{12pt}

Considering an ideal dielectric waveguide (no absorption) with the purpose of transmitting EM waves in the $\hat{z}$ direction, the total field distribution is a sum of continous TEM plane waves.
Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ is possible to study the propagation of the wave along the waveguide using the Helmholtz equation (\ref{eq_helm_P}) or (\ref{eq_helm_lin}).
\vspace{18pt}
Defining $k=\beta$ in eq (\ref{eq_wave}) leads to the following equations:
\begin{subequations}
\begin{align}
	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2-\beta^2\right]F(x,y) = 0 \\
	??? \qquad \qquad \frac{\partial^2A(z,t)}{\partial z^2} + \frac{n^2}{c^2}\frac{\partial^2A(z,t)}{\partial t^2} = 0 \\
	??? \qquad \qquad \frac{\partial^2A(z,t)}{\partial z^2} + k^2n^2\frac{\partial^2A(z,t)}{\partial t^2} = 0
\end{align}
\end{subequations}
\vspace{18pt}
****
\vspace{12pt}

@@

\subsection{Rectangular dielectric waveguides}
In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
For our purpose, due to the thin geometry of the core, modes with the higher effective index are fundamental modes in the height axis.
Only one significant index is then left to describe the order of modes.

@@

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
\begin{equation}
\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right)
\end{equation}
which originates from the behaviour of bound electrons.

@@

The nonlinear component of the induced electric polarization vector, considering significant only the third-order term, is
$$ \textbf{P}_{NL} = \varepsilon_0 \chi^{(3)} \vdots \textbf{E}^3 $$

\vspace{18pt}
****		è necessario verificare conservazione di energia e momento
\vspace{12pt}
\begin{equation}
	\textbf{E} = \frac{1}{2}\hat{x} \sum_{j=1}^4 E_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
	\label{eq_E}
\end{equation}
and the induced electric polarization:
\begin{equation}
	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
	\label{eq_P}
\end{equation}
considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode

\begin{subequations}
\begin{align}
	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{\mathrm{i}\Delta k_z} \right] \\
	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{\mathrm{i}\Delta k_z} \right] \\
	\frac{dA_3}{dz} &= \frac{\mathrm{i}n_L\omega_3}{c}\left[ \left( f_{33} |A_3|^2 + 2 \sum_{k\neq3} f_{3k}|A_k|^2\right)A_3 + 2f_{3412}A_1A_2A_4^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right] \\
	\frac{dA_4}{dz} &= \frac{\mathrm{i}n_L\omega_4}{c}\left[ \left( f_{44} |A_4|^2 + 2 \sum_{k\neq4} f_{4k}|A_k|^2\right)A_4 + 2f_{4321}A_1A_2A_3^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right]
\end{align}
\label{eq_coupled_amplitude}
\end{subequations}

@@

>>>>

\subsubsection*{Solution in linear dielectric medium}
A linear dielectric medium is characterized by a linear relation between the polarization density and the electric field:
\begin{equation}
	\textbf{P} = \varepsilon_0 \chi \textbf{E}
	\label{eq_P_L}
\end{equation}
where $\chi$ is the susceptibility of the medium and $\varepsilon_r \equiv 1+\chi$ is the relative dielectric constant.

@@

Defining the refractive index $n \equiv \sqrt{\varepsilon_r}$ of the material the previous equation (\ref{eq_helm_P}) and using the definition of \textbf{P} as in eq (\ref{eq_P_L})
\begin{equation}
	\nabla^2 \textbf{E} - \frac{n^2}{c^2}\frac{\partial^2 \textbf{E}}{\partial t^2} = 0
	\label{eq_helm_lin}
\end{equation}
Moreover, $n$ represent the ratio between the speed of light in vacuum and in the material $n = c/v$ and it depends on the frequency of the EM wave.

@@

\subsubsection*{Wave equation and modes}
Considering an ideal dielectric waveguide (no absorption) with the purpose of transmitting EM waves in the $\hat{z}$ direction, the total field distribution is a sum of continous TEM plane waves.
Defining the amplitude of the fields as $E(\textbf{r},t) = F(x,y)A(z,t)$ and $k=\beta$ and substituting them in eq (\ref{eq_wave}) leads to the following equation:
\begin{equation*}
	\textbf{E} = \frac{1}{2}\hat{x}\,F(x,y)A(z,t)\,\mathrm{exp}[\mathrm{i}(\beta z-\omega t)] + c.c.
\end{equation*}

The previous equation represents what is called a ``transverse electric" (TE) wave.
A second family of solution could be acquired by defining the sum of TEM wave with the magnetic field always perpendicular to the propagation direction.
This is called a ``transverse magnetic" (TM) wave.

Is then possible to study the propagation of the wave along the waveguide using the Helmholtz equation (\ref{eq_helm_P}) or (\ref{eq_helm_lin}), obtaining the next equations:

\begin{subequations}
\begin{align}
	\frac{\partial^2F(x,y)}{\partial x^2} + \frac{\partial^2F(x,y)}{\partial y^2} + \left[ k_0^2n^2-\beta^2\right]F(x,y) = 0 \\
	\frac{\partial^2A(z,t)}{\partial z^2} + \frac{n^2}{c^2}\frac{\partial^2A(z,t)}{\partial t^2} = 0
	\quad ??? \quad or \quad ??? \quad
	\frac{\partial^2A(z,t)}{\partial z^2} + k^2n^2\frac{\partial^2A(z,t)}{\partial t^2} = 0
\end{align}
\end{subequations}
where $k_0$ is the wavevector in vacuum and $n$ is a function of the position (mainly $x$ and $y$).

\vspace{18pt}
************************************************************************
\vspace{12pt}

These equations, once solved, lead to the distribution of the fields in the plane xy and to their modification along the z axis.

\vspace{18pt}
************************************************************************
\vspace{12pt}

@@

\subsection{Rectangular dielectric waveguides}
In general, in a rectangular dielectric waveguide the classification of modes need two indexes because we have two degrees of freedom.
In Figure (\ref{fig_2dmodes}) is *** a graphical representation of the distribution of the fields in modulus.

@@

For our purpose, due to the thin geometry of the core, modes with the higher effective index are fundamental modes in the height axis.
The first row is of our interest.
Only one significant index is then left to describe the order of modes.

\section{Non-linear optics}
A nonlinear dielectric medium is characterized by a nonlinear relation between \textbf{P} and \textbf{E}, such as
\begin{equation}
	\textbf{P} = \varepsilon_0 \left( \chi^{(1)} \cdot \textbf{E} + \chi^{(2)} : \textbf{E}^2 + \chi^{(3)} \vdots \textbf{E}^3 + \cdots \right)
	\label{eq_P_general}
\end{equation}
which originates from the behaviour of bound electrons.

@@

The nonlinear component of the induced electric polarization vector, considering significant only the third-order term, is
\begin{equation}
	\textbf{P}_{NL} = \varepsilon_0 \chi^{(3)} \vdots \textbf{E}^3
	\label{eq_P_NL}
\end{equation}

\vspace{18pt}
************************************************************************
\vspace{12pt}

\begin{equation}
	\textbf{E} = \frac{1}{2}\hat{x} \sum_{j=1}^4 E_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
	\label{eq_E}
\end{equation}
and the induced electric polarization:
\begin{equation}
	\textbf{P} = \frac{1}{2}\hat{x} \sum_{j=1}^4 P_j \mathrm{exp}[i(\beta_j z - \omega_j t)] + c.c.
	\label{eq_P}
\end{equation}
considering $E_j(\textbf{r}) = F_j(x,y)A_j(z)$ where $F_j$ is the spatial distribution of the mode

\begin{subequations}
\begin{align}
	\frac{dA_1}{dz} &= \frac{\mathrm{i}n_L\omega_1}{c}\left[ \left( f_{11} |A_1|^2 + 2 \sum_{k\neq1} f_{1k}|A_k|^2\right)A_1 + 2f_{1234}A_2^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right] \\
	\frac{dA_2}{dz} &= \frac{\mathrm{i}n_L\omega_2}{c}\left[ \left( f_{22} |A_2|^2 + 2 \sum_{k\neq2} f_{2k}|A_k|^2\right)A_2 + 2f_{2134}A_1^*A_3A_4\mathrm{e}^{+\mathrm{i}\Delta k_z} \right] \\
	\frac{dA_3}{dz} &= \frac{\mathrm{i}n_L\omega_3}{c}\left[ \left( f_{33} |A_3|^2 + 2 \sum_{k\neq3} f_{3k}|A_k|^2\right)A_3 + 2f_{3412}A_1A_2A_4^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right] \\
	\frac{dA_4}{dz} &= \frac{\mathrm{i}n_L\omega_4}{c}\left[ \left( f_{44} |A_4|^2 + 2 \sum_{k\neq4} f_{4k}|A_k|^2\right)A_4 + 2f_{4321}A_1A_2A_3^*\mathrm{e}^{-\mathrm{i}\Delta k_z} \right]
\end{align}
\label{eq_coupled_amplitude}
\end{subequations}

@@

\subsubsection*{Approximate solution}
The previous equations are quite general (they include SPM, XPM in addition to FWM) and require a numerical approach to be solved exactly.
For this reason, we propose an approximate solution to understand the physical implication.
The first approximation is called ``undepleted pump" and consist of assuming the pump waves to be much more intense than the other waves.
As a further simplification, we assume that all overlap integrals are nearly the same
\begin{equation}
	f_{ijkl} \approx f_{ij} \approx \frac{1}{A_{eff}}	\qquad \qquad i,j,k,l = 1,2,3,4
	\label{eq_overlap_approx}
\end{equation}
From this definition follows naturally the nonlinear parameter definition
\begin{equation}
	\gamma_j = \frac{n_2\omega_j}{cA_{eff}} \approx \gamma
	\label{eq_gamma_approx}
\end{equation}
where $\gamma$ is the average value (because frequencies have relatively small differencies).

Using the last two equations and the undepleted pump approximation, (\ref{eq_coupled_amplitude}a) and (\ref{eq_coupled_amplitude}b) are easily solved to obtain the pump fields
\begin{subequations}
\begin{align}
	A_1(z) &= A_1(0)\mathrm{exp}[\mathrm{i}\gamma(P_1 + 2P_2)z] \\
	A_2(z) &= A_2(0)\mathrm{exp}[\mathrm{i}\gamma(P_2 + 2P_1)z]
	\label{eq_pump_sol}
\end{align}
\end{subequations}
where $P_j = |A_j(z=0)|^2$.

Using the same approximations on (\ref{eq_coupled_amplitude}c) and (\ref{eq_coupled_amplitude}d) and replacing eq (\ref{eq_pump_sol}) where needed we obtain two linear coupled equation for signal and idler:
\begin{subequations}
\begin{align}
	\frac{dA_3}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_3 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_4^*] \\
	\frac{dA_4}{dz} &= 2\mathrm{i}\gamma [(P_1 + P_2)A_4 + A_1(0)A_2(0)\mathrm{e}^{-\mathrm{i}\phi}A_3^*]
	\label{eq_sig_idl}
\end{align}
\end{subequations}
where $\phi = [\Delta k - 3\gamma(P_1 + P_2)]z$

\vspace{18pt}
************************************************************************
\vspace{12pt}

The \textit{effective} phase mismatch is therefore given by
\begin{equation}
	\kappa = \Delta k + \gamma(P_1 + P_2)
\end{equation}
